PS753

### 2022-01-30 _academics/ps753/ps753.Rmd
lowercase ps743 you idiot
text

Class work from this class will be listed here as we go. This part has to be done by hand in Distill, unfortunately.

- My ongoing [glossary](../PS753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.

>>>>

Work and assignments from this class will be added here as we go. (This part has to be done by hand in Distill, unfortunately.)

- My ongoing [glossary](../ps753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
